Titeln på avhandlingens språk

### 2022-10-28 implications_optimization.tex
junjues

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figs/EdgeDroid2ExperimentalSetup.png}
    \caption{%
        Experimental setup used to study the implications of the realistic models of human behavior for \ac{WCA}.
        We deploy containerized instances of the client-server loop running the models on a testbed consisting of \num{10} Raspberry Pi clients connected to a cloudlet over a \ac{COTS} \acs{IEEE} \num{802.11}n access point.
    }\label{fig:expsetup}
\end{figure}

@@

\subsection{Energy consumption}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figs/EdgeDroid2ExperimentalSetup.png}
    \caption{%
        Experimental setup used to study the implications of the realistic models of human behavior for \ac{WCA}.
        We deploy containerized instances of the client-server loop running the models on a testbed consisting of \num{10} Raspberry Pi clients connected to a cloudlet over a \ac{COTS} \acs{IEEE} \num{802.11}b/g access point.
    }\label{fig:expsetup}
\end{figure}

@@

\subsection{Optimizing for mean number of samples per step}

In~\cite{Wang2019Towards}, \citeauthor{Wang2019Towards} introduce an adaptive sampling scheme for \ac{WCA} intended to reduce the number of samples processed per step while still meeting application responsiveness bounds.
At every sampling instant \( t \), the scheme adapts the sampling rate \( R(t) \) of the system according to the estimated likelihood of the user having finished the step,
following the formula

\begin{equation}
    R(t) = R_\text{min} + \alpha\left( R_\text{max} - R_\text{min} \right) * CDF(t)
\end{equation}

\( R_\text{max} \) and \( R_\text{min} \) correspond to the maximum and minimum sampling rates of the system, respectively.
\( R_\text{max} \) can directly be assumed to correspond to one over the mean \ac{RTT} of the system, whereas \( R_\text{min} \) needs to either be calculated according to the latency bounds of the system or specified manually.
\( \alpha \) corresponds to a scaling factor and \( t \) to the time of the current sampling instant with respect to the start of the step.
Finally, \( CDF \) corresponds to the \acl*{CDF} of a distribution describing the execution times for the current step; \citeauthor{Wang2019Towards} used a single static Gaussian distribution for all steps in their work.

In the following, we will show the effects of more accurate execution time estimation using our timing models on the performance of this adaptive scheme.
For this, we implement two variants of the adaptive scheme.
The first one corresponds to \citeauthor{Wang2019Towards}'s original design, using a Gaussian distribution fitted to all the execution times collected for~\cite{olguinmunoz:impact2021} for \ac{CDF} calculation.
The second variant instead uses an embedded internal execution time model to keep track of the \acp{TTF} of the system and adjust the distribution of execution times following the state of the timing model.

We proceed to set up an experiment where these sampling scheme variants are deployed on identical, simulated, \num{100}-step tasks.
The execution times for each step are generated by a realistic model parameterized with high neuroticism and without any distribution fitting on the data (this timing model is separate from the internal timing models inside the sampling schemes).
We set \( R_\text{min} \) to \SI{0.5}{\hertz}, \( \alpha \) to \num{3.0}, and the \ac{RTT} of the system to a constant \SI{150}{\milli\second}, and then run \num{90} repetitions of the task for the original design of the sampling scheme as well as for each possible configuration of it with a different parameterization of the timing model.

\begin{figure}
    \centering
    \begin{subfigure}[]{\columnwidth}
        \centering
        \includegraphics[width=.9\textwidth]{figs/new_model/sampling_junjue.png}
        \caption{%
            Mean number of samples per step over a \num{100}-step task, \num{90} independent repetitions per configuration.
            Error bars indicate \SI{95}{\percent} \acp{CI}.
        }
    \end{subfigure}
    \begin{subfigure}[]{\columnwidth}
        \centering
        \includegraphics[width=.9\textwidth]{figs/new_model/diff_sampling_junjue.png}
        \caption{%
            Percentage difference in mean number of samples per step.
            Error bars indicate the \SI{95}{\percent} \acp{CI}, calculated using a two-sided T-test.
        }
    \end{subfigure}
    \caption{Results of parameterizing \textcite{Wang2019Towards}'s adaptive sampling scheme using the realistic timing model.}\label{fig:samples}
\end{figure}

The results of this investigation are presented in \cref{fig:samples}, and they clearly show the potentially dramatic effects of more accurate execution time estimation when optimizing sampling rates.
When using the realistic model for execution time estimation, the sampling scheme achieve between \SI{21}{\percent} and \SI{25}{\percent} better average performance.
This is true even for configurations with low neuroticism which do not exactly match the parameterization of the external timing model driving the execution times for the steps, showing thus the importance of even less-accurate approximations.

\subsection{Optimizing for energy consumption}

### 2022-10-28 model.tex
junjues

The distribution chosen for the second variant described above corresponds to the \ac{exGaussian} distribution.
We've chosen this distribution due to the vast body of research supporting its suitability for the modeling of the timing of human actions~\cite{Rohrer1994analysis,Palmer2011shapes,Marmolejo2022generalised}.

@@

\begin{enumerate}
    \item\label{it:ttftoexectime} Higher \acp{TTF} should result in higher execution times.
    \item\label{it:duration} When subject to a series of steps at the same level of impairment, desired model behavior depends on the impairment:
    \begin{enumerate}
        \item At low \acp{TTF}, the model should speed up; i.e.\ execution times should decrease.
        \item At medium \acp{TTF}, execution times should remain more or less the same.
        \item At high \acp{TTF}, execution times should progressively increase.
    \end{enumerate}
    \item The effects on execution times due to past reductions or improvements in system responsiveness should linger for at least a few steps whenever system responsiveness changes/
    \item\label{it:neuro} Finally, neuroticism should act as a modulating factor for the above effects.
\end{enumerate}

>>>>

The distribution chosen for the second variant described above corresponds to the \ac{exGaussian} distribution.
We've chosen this distribution due to the vast body of research supporting its suitability for the modeling of the timing of human actions~\cite{Rohrer1994analysis,Palmer2011shapes,Marmolejo2022generalised}.
Fitting is done using \ac{MLE}.

@@

\begin{enumerate}
    \item\label{it:ttftoexectime} Higher \acp{TTF} should result in higher execution times.
    \item\label{it:duration} When subject to a series of steps at the same level of impairment, desired model behavior depends on the impairment:
    \begin{enumerate}
        \item At low \acp{TTF}, the model should speed up; i.e.\ execution times should decrease.
        \item At medium \acp{TTF}, execution times should remain more or less the same.
        \item At high \acp{TTF}, execution times should progressively increase.
    \end{enumerate}
    \item The effects on execution times due to past reductions or improvements in system responsiveness should linger for at least a few steps whenever system responsiveness changes.
    \item\label{it:neuro} Finally, neuroticism should act as a modulating factor for the above effects.
\end{enumerate}
